%
\chapter{Acknowledgements}\label{sec:acknowledgement}%
%
    This thesis to a large part is the result not only of my own work but of the collaboration of many people. I could not have succeeded with this project without the support and effort that every one of them invested.\\%
%
    \,\newline%
    This work was not possible without the help of many people. Fist and foremost, I would like to thank my supervisor Prof. Dr. Thomas Klinger, research group leader and mentor Dr. Felix Reimold and Dr. Daihong Zhang for their unending patience and enlightening guidance throughout the many years.\\%
%
    \,\newline%
    My gratitude and best wishes goes to all the scientist and colleagues contributing now, in the past and the far future to the endeavour that is the fusion plasma experiment Wendelstein 7-X. Back before attending university I only dreamt of working with the stellarator myself and contributing a meaningful part to its advancement.\\%
%
    \,\\%
    Most importantly, there is a small group of people that made this possible in the first place and supported me every step of the way. From the bottom of my heart, my sincerest and deepest love to all of you -  my wife, Stella, for sharing the burden more than I would have ever wanted and my parents, for always holding me up and on whose shoulders I stand tall and proud.\\%
%
    \,\newline%
    This work has been carried out within the framework of the EUROfusion Consortium and has received funding from the Euratom research and training programme 2014-2018 and 2019-2020 under grant agreement No 633053. The views and opinions expressed herein do not necessarily reflect those of the European Commission.
%